Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-06 ms.tex
filled in goodness-of-fit figure caption

The posterior sampling framework thus far described also affords us an
opportunity to evaluate the goodness-of-fit for competing dust SED models, and 
thereby cross-check the conclusions of our correlation slope analysis in
$\S$\ref{sec:global}. The basic idea will be to continue sampling the posterior
of Equation \ref{eqn:post}, but at low resolution ($N_{side}$=64), including 
all HFI bands as well as DIRBE 100$\mu$m, 140$\mu$m and 240$\mu$m, and 
switching to a uniform prior on $T_2$. Under these circumstances, the 
chi-squared corresponding to the best-fit parameters for each pixel, termed 
$\chi^2_p$, is simply $-2 \times log(P_{max})$. We will refer to the
per-pixel chi-squared per degree of freedom as $\chi^2_{p, \nu}$.
% maybe invent a term chi^2_p or something to 
% reduce potential confusion caused by notation

\begin{figure}
\begin{center}
\epsfig{file=chi2_dirbe.eps, width=3.3in}
\caption{\label{fig:chi2_dirbe} Comparison of goodness-of-fit, 
$\chi^2_{\nu}$=$\langle \chi^2_p \rangle$ for various dust SED models.}
\end{center}
\end{figure}

@@

>>>>

The posterior sampling framework thus far described also affords us an
opportunity to evaluate the goodness-of-fit for competing dust SED models, and 
thereby cross-check the conclusions of our correlation slope analysis in
$\S$\ref{sec:global}. The basic idea will be to continue sampling the posterior
of Equation \ref{eqn:post}, but at low resolution ($N_{side}$=64), including 
all HFI bands as well as DIRBE 100$\mu$m, 140$\mu$m and 240$\mu$m, and 
switching to a uniform prior on $T_2$. Under these circumstances, the 
chi-squared corresponding to the best-fit parameters for each pixel, termed 
$\chi^2_p$, is simply $-2 \times log(P_{max})$. We will refer to the
per-pixel chi-squared per degree of freedom as $\chi^2_{p, \nu}$.

\begin{figure}
\begin{center}
\epsfig{file=chi2_dirbe.eps, width=3.3in}
\caption{\label{fig:chi2_dirbe} Comparison of goodness-of-fit, 
$\chi^2_{\nu}$=$\langle \chi^2_{p, \nu} \rangle$ for various dust SED models. 
For single-MBB models with spatially constant $\beta$, we varied $\beta$ 
between 1 and 2 (x axis), achieving reduced chi-squared $\chi^2_{\nu}$ shown by
the black line, with $\beta$=1.57 providing the best fit. Horizontal lines 
indicate $\chi^2_{\nu}$ for other dust SED models considered, including the 
FDS99 best-fit model and our best-fit \PLANCK+DIRBE model from 
$\S$\ref{sec:global}. The minimum $\chi^2_{\nu}$ was achieved with
two-componenent `model 2' from Table \ref{tab:global} (horizontal magenta 
line).}
\end{center}
\end{figure}

@@

% say that, becuase such little improvement for two-component versus
% single MBB in this analysis, we include a single-MBB beta = 1.57 fit in
% our data release ???
